---
title: "Code-Environment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{05-Code-Env}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## How are code blocks handled by texor

Pandoc naturally converts verbatim environment easily, however the redefination 
of other commands such as `example`, `example*`, `Sinput` etc to verbatim does not work well in pandoc.

Hence Texor package uses the stream editor to search find and replace matching code environments to verbatim before pandoc touches it.

This way the the code is not lost in conversion, also a pandoc extension is used to add attributes to the markdown code using 
'fenced_code_attributes`

### Supported RJ-article (LaTeX) code environment:

```{r, echo = FALSE, results = 'asis'}
library(knitr)
table <- data.frame(
              "example" = c("example, example*"),
              "S-series" = c("Sin, Sout, Scode,Sinput,Soutput"),
              "special-verbatim" = c("smallverbatim, boxedverbatim"))
kable(table, caption =  "Code Environment support in texor")
```
Note that any special markup (like font-size, font-style) bought by any of these code environments will be lost,
However the retained text will have syntax highlighting (for R by default, if you want to change the syntax highlighting, change the language in the markdown source code formed)
