---
title: "How to use bibliography tools"
author: Abhishek Ulayil
output: rmarkdown::html_vignette 
vignette: >
  %\VignetteIndexEntry{bibliography}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(texor)
```

`Texor` is a toolkit package to help with the conversion of documents. To enable a bibliography to be included in these web articles, `texor` has several functions to address different needs.

1. `rjtools::rjournal_web_article` accepts bibliography in BibTex, so if you have written or included bibliography as BibTex, it would be very convenient to include it in your LaTeX source file.

2. If you have already written or included the bibliography as BibLaTeX within the LaTeX source code. Then you need to convert the BibLaTeX to BibTeX using the `texor::handle_bibliography()` function.

## How to convert embedded LaTeX bibliography to BibTeX

Here is an sample where the function `texor::handle_bibliography()` will search for RJwrapper file in the directory and read the nested LaTeX file in search of bibliography. If the bibliography is found to be linked as BibTeX file, the function will exit. If the bibliography is embedded then it will convert to a minimal BibTeX format.

```{r bbl2bib, echo=TRUE}
wd <-  system.file("examples/bibliography", package = "texor") 
texor::handle_bibliography(wd)
# the bib file is generated live
bib_file <- system.file("examples/bibliography/example.bib", package = "texor")
readLines(bib_file)
```
