---
title: "TexoR"
subtitle: '**Convert Old LaTeX files to RMd/HTML**'
author:  
  # see ?rjournal_article for more information
  - name: Abhishek Ulayil
    affiliation: (proposed)GSoC Contributer
    address:
    - Somewhere in Mumbai
    - India
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TexoR)
```

# Introduction 
\CRANpackage{TexoR} is a proposed package that can help in converting old LaTeX based documents, research papers to HTML through intermediate conversions. This is particularly a problem for pre 2008 R Research papers where R journal was not available and hence modern compatibility to export a HTML file was missed out.
    To bring these documents online HTML based webpages are a much better alternative as opposed to PDFs and to solve the lack of web versions TexoR will provide a mechanism.  
